The Ontological Modal Collapse \\ as a Collapse of the Square of Opposition

### 2016-03-25 Papers/2014/Universalis/ModalCollapse.tex
Clarify statement about the need for ontological axioms for teh characterization of larger classes modally collapsing propositions.

An easy corollary of the second fact above is that any ontological argument relying on Lemma \textbf{L2} will necessarily lead to a modal collapse for all propositions that are logically equivalent to God's existence. The third and fourth facts above indicate that to prove that the modal collapse holds for a larger class of propositions would require using axioms specific to the ontological argument.

% \marginpar{@Bruno: Shall we respond here to the
%  rewievers criticism?}

>>>>

An easy corollary of the second fact above is that any ontological argument relying on Lemmas \textbf{L1} and \textbf{L2} will necessarily lead to a modal collapse for all propositions that are logically equivalent to God's existence. The third and fourth facts indicate that characterizations of larger classes of propositions for which the modal collapse holds require using axioms specific to the variant of the ontological argument under consideration, as in the case of \textbf{A:MC}.
